---
title: "minifying"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{minifying}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`{minifying}` is a `{shiny}` application that helps minifying css, html, javascript and JSON files. 
It relies on the `{minifyr}` package, which is a wrapper around `node-minify`. 

The core backend of this application is divided into three functions:

```{r echo = FALSE}
library(minifyr)
funs <- ls("package:minifyr", pattern = "minifyr_js_")
```

### `guess_minifier()`

This function tries to guess the minifier to use, based on the file extension:

```{r echo = FALSE}
library(minifyr)
guess_minifier <- function(file){
  # We'll start by getting the file extension
  ext <- tools::file_ext(file)
  # Check that the extension is correct, if not, return early
  # It's important to do this kind of check also on the server side 
  # As HTML manual tempering would allow to also send other type of files
  if (
    ! ext %in% c("js", "css", "html", "json")
  ){
    # Return early
    return(list())
  }
  # We'll then retrieve the available pattern based on the extension
  patt <- switch(
    ext, 
    js = "minifyr_js_.+",
    html = "minifyr_html_.+",
    css = "minifyr_css_.+",
    json = "minifyr_json_.+"
  )
  # List all the available functions to minify the file
  list(
    file = file,
    ext = ext,
    # We return this pattern so that it will be used to update the selectInput that 
    # is used to select an algo
    pattern = patt, 
    functions = grep(patt, names(loadNamespace("minifyr")), value = TRUE)
  )
  
}
```

```{r}
# minifyr comes with a series of examples, so we can use them as tests
guess_minifier(
  minifyr_example("css")
)
guess_minifier(
  minifyr_example("js")
)
guess_minifier(
  minifyr_example("html")
)
guess_minifier(
  minifyr_example("json")
)
# Try with a non valid extension
guess_minifier(
  "path/to/text.docx"
)
```


### `compress()`

`compress()` perform the minification.

```{r echo = FALSE}
compress <- function(algo, selection){
  # Creating a tempfile using our algo object
  tps <- tempfile(fileext = sprintf(".%s", algo$ext))
  # Getting the function with the selection
  converter <- get(
    grep(selection, algo$functions, value = TRUE)
  )
  # Do the conversion
  converter(algo$file, tps)
  # Return the temp file
  return(tps)
}

algo <- guess_minifier(
  minifyr_example("js")
)
```


```{r}
compress(
  algo = algo, 
  selection = "babel"
)
```

### `compare()`

`compare()` compares the size of two files, so that we can evaluate the size gain from the minification (but it can also be used with any other files).

```{r echo = FALSE}
compare <- function(original, minified){
  # Get the file size of both
  original <- fs::file_info(original)$size
  minified <- fs::file_info(minified)$size
  return(original - minified)
}
```

```{r}
compare(
  minifyr_example("js"), 
  minifyr_example("html")
)
```

### Full workflow

These three functions are designed to be combined:

```{r}
algo <- guess_minifier(
  minifyr_example("js")
)

compressed <- compress(
  algo = algo, 
  selection = "babel"
)
compare(
  minifyr_example("js"), 
  compressed
)
```